### 2013-05-26 poster/poster.tex
haifa logo
cmu logo
design

\usepackage{times}
\usepackage{calc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{url}
\usepackage{tipa}
%\usepackage{biblatex}

@@

\usepackage{helvet}
\usepackage{palatino}
\usepackage{listings}
\newcommand{\captionfont}{\footnotesize}
\newcommand{\hl}[1]{\color{red}{#1}}
%\newcommand{\textgl}[1]{``#1''}
%\newcommand{\word}[2]{\textnl{#1} \textgl{#2}}
%\newcommand{\gloss}[3]{\textnl{#1} (\textnl{#2}) \textgl{#3}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Here starts the poster
%%%---------------------------------------------------------------------------
%%% Format it to your taste with the options
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\typeout{Poster Starts}
\background{
  \begin{tikzpicture}[remember picture,overlay]%
    \draw (current page.north west)+(-2em,-0em) node[anchor=north west] {\hspace{-2em}\includegraphics[height=1.1\textheight]{silhouettes_background}};
  \end{tikzpicture}%
}
\definecolor{silver}{cmyk}{0,0,0,0.3}
\definecolor{yellow}{cmyk}{0,0,0.9,0.0}
\definecolor{reddishyellow}{cmyk}{0,0.22,1.0,0.0}
\definecolor{black}{cmyk}{0,0,0.0,1.0}
\definecolor{darkYellow}{cmyk}{0,0,1.0,0.5}
\definecolor{darkSilver}{cmyk}{0,0,0,0.1}

@@

\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=0.8em,
  % Color style
  bgColorOne=lightestcyan, %lighteryellow,
  bgColorTwo=lighterblue, %lightestyellow,
  borderColor=darkpurple, %reddishyellow,
  headerColorOne=blue, %yellow,
  headerColorTwo=darkpurple, %reddishyellow,
  headerFontColor=black,
  boxColorOne=lighterblue, %lightyellow,
  boxColorTwo=lighterblue, %lighteryellow,
  % Format of textbox
  textborder=rounded, %roundedleft,
  % Format of text header
  eyecatcher=yes,
  headerborder=closed,
  headerheight=0.1\textheight,
  headershape=rounded, %roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {%\begin{minipage}{7em}
\includegraphics[width=9em]{img/CarnegieMellonUniversity}\\
%\end{minipage}
} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\bf %Sans Serif
  %\bf% Serif
  Identifying the native language of non-native English writers
  }
    % Authors
  {\large\sl %Sans Serif
  % Serif
  Chris Dyer, Manaal Faruqui, Nathan Schneider, Yulia Tsvetkov, Language Technologies Institute,
  Carnegie Mellon University, Pittsburgh, PA
  \large
  \\Noam Ordan, Naama Twitto, Shuly Wintner,
  Department of Computer Science,University of Haifa, Haifa, Israel
  }
  % University logo clip=true, trim=l b r t,
  {  \includegraphics[height=5.1em]{img/University_of_Haifa_logo} %logo1
  }
 % {  \includegraphics[height=5.1em]{img/logo1}
  %}

@@

\centering\small
\vspace{4pt}
\textbf{Firstly the employers live more savely because they are going to have more money to spend for luxury .}\\[14pt]

\begin{tabular}{p{6em}p{15em}p{15em}}
 & \multicolumn{1}{c}{\bf Presence} & \multicolumn{1}{c}{\bf Considered alternatives/edits} \\
\hline
\bf Characters
& 
\smaller[.5]
 \begin{tabular}{@{}p{12em}p{5em}@{}} 
   "FreqChar\_l\_y\_ ":&$\log{2+1}$\\"CharPrompt\_P5\_g\_o\_i":&$\log{1+1}$\\"Punct\_period":&$\log{1+1}$ %\\"MFChar\_e\_ ":&$\log{1+1}$
 \end{tabular} 
& 
\smaller[.5]
 \begin{tabular}{@{}p{12em}p{5em}@{}} 
   "Misspell\_DeleteP\_p\_.":&$1.0$\\"Misspell\_InsertP\_p\_,":& $1.0$\\"Misspell\_MID:SUBST:v:f":&$\log{1+1}$\\"Misspell\_SUBST:v:f":&$\log{1+1}$
 \end{tabular} \\
\hline
\bf Words 
& 
\smaller[.5]
 \begin{tabular}{@{}p{12em}p{5em}@{}}
    "DocLen\_":&$\log{19+1}$\\"MeanWordRank":&$422.6$\\"CohMarker\_because":&$\log{1+1}$\\"MostFreq\_have":&$\log{1+1}$\\"PosToken\_last\_luxury":&$\log{1+1}$\\ "Pronouns\_they":&$\log{1+1}$
 \end{tabular}
& 
\smaller[.5]
 \begin{tabular}{@{}p{12em}p{5em}@{}}
   "Misspell\_safely":&$\log{1+1}$\\"Restore\_Match\_p\_to":&$0.5$\\"Restore\_Delete\_p\_to":&$0.5$\\"Restore\_Delete\_p\_are":&$1.0$\\"Restore\_Delete\_p\_because":&$1.0$\\"Restore\_Delete\_p\_for":&$1.0$
 \end{tabular} \\
\hline
\bf{POS} 
& 
\smaller[.5]
\begin{tabular}{@{}p{12em}p{5em}@{}}
  "POS\_VBP\_VBG\_TO":&$\log{1+1}$\\"POS\_p\_VBP\_VBG\_TO":&$0.059$
\end{tabular} \\
\hline
\bf Words + POS 
& 
\smaller[.5]
\begin{tabular}{@{}p{12em}p{5em}@{}}
  "CxtFxn\_VBP\_VBG\_to":&$\log{1+1}$\\"CxtFxn\_more\_RB":&$\log{1+1}$
\end{tabular} \\
\hline

@@

\end{tabular} \\\\[14pt]

\end{tabular}

\begin{tabular}{p{10em}p{32em}}
  \multicolumn{1}{c}{\bf Brown clusters} & \multicolumn{1}{c}{\bf Words in cluster}\\\hline
 C\_1111101111110   & investors customers patients employees consumers users citizens shareholders clients individuals managers buyers viewers \textbf{employers} guests readers immigrants taxpayers humans donors households homeowners competitors travelers audiences borrowers shoppers offenders physicians creditors subscribers stockholders sellers entrepreneurs advertisers applicants motorists tenants builders smokers strangers collectors listeners savers retirees outsiders travellers bidders bondholders patrons\\ \hline

@@

 \end{tabular} 
% \begin{center}
%Some of the features extracted for an L1 German sentence.
%\end{center}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Results%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Results}{name=results,column=1.15,span=1.85,below=example}{
\begin{center}
\small
\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r||c|c|}
      \hline
 \multirow{2}{*}{} &ARA & CHI & FRE & GER & HIN & ITA & JPN &  KOR & SPA &  TEL &  TUR	& \bf P(\%) & \bf R(\%)  \\			
      \hline\hline
ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 & 80.8 & 80.0  \\
CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1 & 88.9 & 80.0  \\
\hline
FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3 & 86.2 & 81.0  \\
GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 87.7 & 93.0  \\
\hline
HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4 & 74.8 & 77.0  \\
ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2 & 82.1 & 87.0   \\
\hline
JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 & 78.4 & 87.0 \\
KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0 & 80.2 & 81.0  \\
\hline
SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5 & 77.2 & 78.0  \\
TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3 & 85.9 & 73.0   \\
%\hline
TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80 & 76.9 & 80.0   \\
			\hline%\hline
\end{tabular}
\end{center}
\begin{center}
Official test set confusion matrix with the full model. Accuracy on the test set is 81.5\%\\
\end{center}

@@

\begin{center}
\begin{tabular}{|l|c|c|c|}
      \hline
 \multirow{2}{*} {} Main features & \# Params 	& Accuracy(\%)	\\				
       \hline\hline
\feat{POS} & 540,947 & 55.18 \\
+ \feat{FreqChar} & 1,036,871 & 79.55 \\ 
\quad + \feat{CharPrompt} & 2,111,175 & 79.82 \\ 
\qquad + \feat{Brown} & 5,664,461 & 81.09 \\
			\hline%\hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{|l|c|c|c|}
      \hline
 \multirow{2}{*} {} Additional features & \# Params 	& Accuracy(\%)	\\				
       \hline\hline
\textsc{main} & 5,664,461 & 81.09 \\
%\textsc{main} + \feat{Position} & 6,153,015 & 81.00 \\
\textsc{main} + \feat{PsvRatio} & 5,664,472 & 81.00 \\
\textsc{main} + \feat{DocLen} & 5,664,472 & 81.09  \\
%\textsc{main} + \feat{Pron} & 5,664,736 & 81.09  \\
\textsc{main} + \feat{Punct} & 5,664,604 & 81.09  \\
\textsc{main} + \feat{Misspell} & 5,799,860 & 81.27  \\
\textsc{main} + \feat{Restore} & 5,682,589 & 81.36  \\
\textsc{main} + \feat{CxtFxn} & 7,669,684 & 81.73 \\
\textsc{full model} & - & {\bf 84.55} \\

>>>>

%\usepackage{times}
\usepackage{calc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{url}
\usepackage{tipa}
%\usepackage{biblatex}

@@

\usepackage{fourier} % utopia font
\renewcommand*\sfdefault{uop} % optima font
%\usepackage{palatino}
\usepackage{listings}
\newcommand{\captionfont}{\footnotesize}
\newcommand{\hl}[1]{\color{red}{#1}}
%\newcommand{\textgl}[1]{``#1''}
%\newcommand{\word}[2]{\textnl{#1} \textgl{#2}}
%\newcommand{\gloss}[3]{\textnl{#1} (\textnl{#2}) \textgl{#3}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Here starts the poster
%%%---------------------------------------------------------------------------
%%% Format it to your taste with the options
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\typeout{Poster Starts}
\background{
  \begin{tikzpicture}[remember picture,overlay]%
    \draw (current page.north west)+(-2em,-0em) node[anchor=north west] {\hspace{-2em}\includegraphics[height=1.1\textheight]{silhouettes_background}};
  \end{tikzpicture}%
}
\definecolor{silver}{cmyk}{0,0,0,0.5}
\definecolor{lightgray}{cmyk}{0,0,0,0.05}
\definecolor{yellow}{cmyk}{0,0,0.9,0.0}
\definecolor{reddishyellow}{cmyk}{0,0.22,1.0,0.0}
\definecolor{black}{cmyk}{0,0,0.0,1.0}
\definecolor{darkYellow}{cmyk}{0,0,1.0,0.5}
\definecolor{darkSilver}{cmyk}{0,0,0,0.1}

@@

\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1.4em,
  % Color style
  bgColorOne=white, %lighteryellow,
  bgColorTwo=white, %lightestyellow,
  borderColor=lightgray, %reddishyellow,
  headerColorOne=red, %yellow,
  headerColorTwo=darkpurple, %reddishyellow,
  headerFontColor=white,
  boxColorOne=lightgray, %lightyellow,
  boxColorTwo=lightgray, %lighteryellow,
  % Format of textbox
  textborder=rounded-small, %roundedleft,
  % Format of text header
  eyecatcher=yes,
  headerborder=closed,
  headerheight=0.1\textheight,
  headershape=rounded, %roundedright,
  headershade=plain,
  headerfont=\large\bf\sc\textsf, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=1pt
}
  % Eye Catcher
  {%\begin{minipage}{7em}
\includegraphics[width=9em]{img/cmu_logo}\\
%\end{minipage}
} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\bf %Sans Serif
  %\bf% Serif
  \textsf{Identifying the L1 of Non-native Writers: The CMU-Haifa System}
  }
    % Authors
  {\large %\it %Sans Serif
  % Serif
  Yulia Tsvetkov$\overset{^\textsc{c}}{\textrm{,}}$ Naama Twitto$\overset{^\textsc{h}}{\textrm{,}}$ Nathan Schneider$\overset{^\textsc{c}}{\textrm{,}}$ Noam Ordan$\overset{^\textsc{h}}{\textrm{,}}$ 
  Manaal Faruqui$\overset{^\textsc{c}}{\textrm{,}}$ Victor Chahuneau$\overset{^\textsc{c}}{\textrm{,}}$ Shuly Wintner$\overset{^\textsc{h}}{\textrm{,}}$ and Chris Dyer$\overset{^\textsc{c}}{\textrm{}}$
  \\
  Language Technologies Institute,
  \textbf{C}arnegie Mellon University, Pittsburgh, PA
  $\bullet$ Department of Computer Science, University of \textbf{H}aifa, Haifa, Israel
  }
  % University logo clip=true, trim=l b r t,
  {  \includegraphics[height=5.1em]{img/haifa_univ_logo} %logo1
  }
 % {  \includegraphics[height=5.1em]{img/logo1}
  %}

@@

\vspace{4pt}
\begin{center}
\textsf{\large Firstly the employers live more savely because they~are~going~to~have~more~money~to~spend~for~luxury~.}
\end{center}
\hspace{1em}Some of the features extracted:

\begin{center}\small
\begin{tabular}{p{6.5em}p{17em}p{17em}}
 & \multicolumn{1}{c}{\bf Presence} & \multicolumn{1}{c}{\bf Considered alternatives/edits} \\
\hline
\bf Characters
& 
\smaller[.5]
 \begin{tabular}{p{12em}p{5em}} 
   "FreqChar\_l\_y\_ ":&$\log{2+1}$\\"CharPrompt\_P5\_g\_o\_i":&$\log{1+1}$\\"Punct\_period":&$\log{1+1}$ %\\"MFChar\_e\_ ":&$\log{1+1}$
 \end{tabular} 
& 
\smaller[.5]
 \begin{tabular}{p{12em}p{5em}} 
   "Misspell\_DeleteP\_p\_.":&$1.0$\\"Misspell\_InsertP\_p\_,":& $1.0$\\"Misspell\_MID:SUBST:v:f":&$\log{1+1}$\\"Misspell\_SUBST:v:f":&$\log{1+1}$
 \end{tabular} \\
\hline
\bf Words 
& 
\smaller[.5]
 \begin{tabular}{p{12em}p{5em}}
    "DocLen\_":&$\log{19+1}$\\"MeanWordRank":&$422.6$\\"CohMarker\_because":&$\log{1+1}$\\"MostFreq\_have":&$\log{1+1}$\\"PosToken\_last\_luxury":&$\log{1+1}$\\ "Pronouns\_they":&$\log{1+1}$
 \end{tabular}
& 
\smaller[.5]
 \begin{tabular}{p{12em}p{5em}}
   "Misspell\_safely":&$\log{1+1}$\\"Restore\_Match\_p\_to":&$0.5$\\"Restore\_Delete\_p\_to":&$0.5$\\"Restore\_Delete\_p\_are":&$1.0$\\"Restore\_Delete\_p\_because":&$1.0$\\"Restore\_Delete\_p\_for":&$1.0$
 \end{tabular} \\
\hline
\bf{POS} 
& 
\smaller[.5]
\begin{tabular}{p{12em}p{5em}}
  "POS\_VBP\_VBG\_TO":&$\log{1+1}$\\"POS\_p\_VBP\_VBG\_TO":&$0.059$
\end{tabular} \\
\hline
\bf Words + POS 
& 
\smaller[.5]
\begin{tabular}{p{12em}p{5em}}
  "CxtFxn\_VBP\_VBG\_to":&$\log{1+1}$\\"CxtFxn\_more\_RB":&$\log{1+1}$
\end{tabular} \\
\hline

@@

\end{tabular} \\[4pt]

\end{tabular}
\end{center}

\begin{center}\small
\begin{tabular}{p{8em}p{40em}}
  \multicolumn{1}{c}{\bf Brown clusters} & \multicolumn{1}{c}{\bf Words in cluster}\\\hline
 C\_1111101111110   & investors customers patients employees consumers users citizens shareholders clients individuals managers buyers viewers \textbf{employers} guests readers immigrants taxpayers humans donors households homeowners competitors travelers audiences borrowers shoppers offenders physicians creditors subscribers stockholders sellers entrepreneurs advertisers applicants motorists tenants builders smokers strangers collectors listeners savers retirees outsiders travellers bidders bondholders patrons\\ \hline

@@

 \end{tabular}
\end{center} 
% \begin{center}
%Some of the features extracted for an L1 German sentence.
%\end{center}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Results%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Results}{name=results,column=1.15,span=1.85,below=example}{
\begin{center}
\small
\begin{tabular}{r|r|r|r|r|r|r|r|r|r|r|r||c|c|}
      %\hline
 \multicolumn{1}{c}{} & \multicolumn{1}{c}{ARA} & \multicolumn{1}{c}{CHI} & \multicolumn{1}{c}{FRE} & \multicolumn{1}{c}{GER} 
 & \multicolumn{1}{c}{HIN} & \multicolumn{1}{c}{ITA} & \multicolumn{1}{c}{JPN} &  \multicolumn{1}{c}{KOR} & \multicolumn{1}{c}{SPA} 
 &  \multicolumn{1}{c}{TEL} & \multicolumn{1}{c}{TUR}	& \multicolumn{1}{c}{\bf P(\%)} & \multicolumn{1}{c}{\bf R(\%)}  \\			
      \cline{2-14} %\hline
ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 & 80.8 & 80.0  \\
CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1 & 88.9 & 80.0  \\
\cline{2-14}
FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3 & 86.2 & 81.0  \\
GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 87.7 & 93.0  \\
\cline{2-14}
HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4 & 74.8 & 77.0  \\
ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2 & 82.1 & 87.0   \\
\cline{2-14}
JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 & 78.4 & 87.0 \\
KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0 & 80.2 & 81.0  \\
\cline{2-14}
SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5 & 77.2 & 78.0  \\
TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3 & 85.9 & 73.0   \\
%\hline
TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80 & 76.9 & 80.0   \\
			\cline{2-14}%\hline
\end{tabular}
\end{center}
\begin{center}
Official test set confusion matrix with the full model. Accuracy on the test set is 81.5\%.\\
\end{center}

@@

\begin{center}\small
\begin{tabular}{|l|r|c|}
      %\hline
 \multicolumn{1}{p{9em}}{Main features} &  \multicolumn{1}{c}{\# Params}	&  \multicolumn{1}{c}{Accuracy(\%)}	\\				
       \hline %\hline
\feat{POS} & 540,947 & 55.18 \\
+ \feat{FreqChar} & 1,036,871 & 79.55 \\ 
\quad + \feat{CharPrompt} & 2,111,175 & 79.82 \\ 
\qquad + \feat{Brown} & 5,664,461 & 81.09 \\
			\hline%\hline
\end{tabular}
\end{center}

\begin{center}\small
\begin{tabular}{|l|c|c|}
      %\hline
 \multicolumn{1}{p{9em}}{Additional features} & \multicolumn{1}{c}{\# Params} & \multicolumn{1}{c}{Accuracy(\%)}	\\				
       \hline %\hline
\textsc{main} & 5,664,461 & 81.09 \\
%\textsc{main} + \feat{Position} & 6,153,015 & 81.00 \\
\textsc{main} + \feat{PsvRatio} & 5,664,472 & 81.00 \\
\textsc{main} + \feat{DocLen} & 5,664,472 & 81.09  \\
%\textsc{main} + \feat{Pron} & 5,664,736 & 81.09  \\
\textsc{main} + \feat{Punct} & 5,664,604 & 81.09  \\
\textsc{main} + \feat{Misspell} & 5,799,860 & 81.27  \\
\textsc{main} + \feat{Restore} & 5,682,589 & 81.36  \\
\textsc{main} + \feat{CxtFxn} & 7,669,684 & 81.73 \\
\textsc{full model} & - & {\bf 84.55} \\
